HO unification from object language to meta language

### 2024-04-03 paper/main.tex
Proof of lemma 2.8 for eta links

\begin{corollary}
  The \rhs of any \linketa has exactly one lambda abstraction, hence
  the rule above respects \cref{inv:link-eta-right}.
\end{corollary}

@@

TODO: prove \cref{prop:nf}: we never commit a \maybeeta{} term in
$\sigma$ since we run \Ue{} only when we know that the 
terms are no more \maybeeta, and when \lhs is no more a variable or \rhs is 
no more a \maybeeta, the link is removed from \linkStore.

>>>>

\begin{corollary}
  The \rhs of any \linketa has exactly one lambda abstraction, hence
  the rule above respects \cref{inv:link-eta-right}.
  \label{cor:rhs-eta-onelamb}
\end{corollary}

@@

\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetaleft is between
  terms in $\wellb$  
  \label{lemma:unif-eta-1}
\end{lemma}

\begin{proof}[Proof sketch]
  Let $\sigma$ be the substitution, such that $\wellb(\sigma)$. $\lhs \in
  \sigma$, therefore $\wellb(\lhs)$. By \cref{def:progressetaleft}, if 1) \lhs is
  a name, a constant of an application, then, \lhs is unified with the
  $\eta$-reduced term $t$ obtain from \rhs. By \cref{cor:rhs-eta-onelamb}, \rhs
  has one lambda, therefore $\wellb(t)$. Otherwise, 2) \lhs has \elpiIn{lam} as
  functor, \rhs should not be an $\eta$-expansion ans, so, $\wellb(\rhs)$. In
  both cases, unification is performed between terms in \wellb.
\end{proof}

\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetaright is between
  terms in \wellb.
  \label{lemma:unif-eta-2}
\end{lemma}

\begin{proof}[Proof sketch]
  \lhs is variable, and, by \cref{def:progressetaright}, \rhs is either no more
  a \maybeeta, i.e. \rhs is not a $\eta$-expansion and, so, $\wellb(\rhs)$.
  Otherwise, \rhs can reduce to a term which cannot be a $\eta$-expansion, and,
  so, $\wellb(\rhs)$. In both cases, unification is done between terms in
  \wellb.
\end{proof}

\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetadedup is between
  terms in \wellb.
  \label{lemma:unif-eta-3}
\end{lemma}

\begin{proof}
  Trivial, since the unification is done between unification variables, which
  are by definition in \wellb.
\end{proof}

\begin{lemma}
  \Cref{prop:nf} holds, i.e., given a substitution $\sigma$ and a \linketa $l$,
  after the activation of $l$, $\wellb(\sigma)$ holds.
\end{lemma}

\begin{proof}[Proof sketch]
  By \cref{lemma:unif-eta-1,lemma:unif-eta-2,lemma:unif-eta-3}, every
  unification performed by the activation of a \linketa is performed between
  terms in \wellb, therefore, the substitution remains \wellb.
\end{proof}
